---
title: "SLAS2_Stats_Notebook"
output: html_SLAS2_Stats_Notebook
---
Validation of Junctions classification
```{r}
confusionMatrix(as_factor(JValidConfusion$AgreedT),as_factor( JValidConfusion$Predicted))

confusionMatrix(as_factor(JValidConfusion$AgreedT),as_factor( JValidConfusion$`Assessor 2`))

confusionMatrix(as_factor(JValidConfusion$AgreedT),as_factor( JValidConfusion$Assessor1))
```

Stats Cell Act Class Analysis
```{r}
CellAct_Stats <-Master_D12_Cl  %>% 
group_by(Experiment,Cell_Type,Treatment, Replicate, Img_N, Img_Nuclei_N, Cell_Act_Cl) %>%
summarise(Counts = length(Cell_Act_Cl))%>%
mutate(Perc = Counts / sum(Counts)*100)

Summary_CellAct <- ddply(CellAct_Stats, c("Cell_Type", "Treatment", "Cell_Act_Cl"), summarise,
               n= length(Perc),           
               mean = mean(Perc),
               sd   = sd(Perc))
Summary_CellAct
```
Stats Cell Cycle Analysis By Cluster
```{r}
CellCycle_Stats_Cluster <-Master_D12_Cl  %>% 
group_by(Experiment, Cell_Type,Treatment, Replicate, Cluster_ID, Cell_Cycle) %>%
summarise(Counts = length(Cell_Cycle))%>%
mutate(Perc = Counts / sum(Counts)*100)

Summary_CellCycle_Cluster <- ddply(CellCycle_Stats_Cluster, c("Cell_Type", "Treatment", "Cluster_ID", "Cell_Cycle"), summarise,
               n= length(Perc),           
               mean = mean(Perc),
               sd   = sd(Perc))
Summary_CellCycle_Cluster
```

Cell In colonies
```{r}
Master_D12_Cl$Colony <- ifelse(Master_D12_Cl$Cluster_ID %in% c(1,2), "IC","NIC")
```

Stats Cell Cycle Analysis By Colony
```{r}
CellCycle_Stats_Colony <-Master_D12_Cl%>% 
group_by(Experiment, Cell_Type, Treatment, Replicate, Colony, Cell_Cycle) %>%
summarise(Counts = length(Cell_Cycle))

Summary_CellCycle_Colony <- ddply(CellCycle_Stats_Colony, c("Cell_Type", "Treatment",  "Colony", "Cell_Cycle"), summarise,
                n= sum(Counts),           
                Perc = Counts/n*100,
                sd   = sd(Perc))
Summary_CellCycle_Colony
```

Stats Cell Cycle Analysis
```{r}
CellCycle_Stats <-Master_D12_Cl  %>% 
group_by(Experiment,Cell_Type,Treatment, Replicate, Img_N, Img_Nuclei_N, Cell_Cycle) %>%
summarise(Counts = length(Cell_Cycle))%>%
mutate(Perc = Counts / sum(Counts)*100)

Summary_CellCycle <- ddply(CellCycle_Stats, c("Cell_Type", "Treatment", "Cell_Cycle"), summarise,
               n= length(Perc),           
               mean = mean(Perc),
               sd   = sd(Perc))
Summary_CellCycle
```

Stats summary for dividing cells 2
```{r}
library(reshape2)
S_Cell_Cy_Div2 <- dcast(CellCycle_Stats, Experiment+Cell_Type + Treatment+Replicate+Img_N+ Img_Nuclei_N ~ Cell_Cycle, value.var="Perc")
S_Cell_Cy_Div2[is.na(S_Cell_Cy_Div2)] <-0
S_Cell_Cy_Div2$Dividing <- (S_Cell_Cy_Div2$'G2/M'+S_Cell_Cy_Div2$LM)
S_Cell_Cy_Div2$Hi_prolif <- ifelse(S_Cell_Cy_Div2$Dividing >= 20, 1, 0)
S_Cell_Cy_Div2

Summary_CC_Div2 <- ddply(S_Cell_Cy_Div2, c("Cell_Type", "Treatment"), summarise,
               n= length(Dividing),           
               mean = mean(Dividing),
               sd   = sd(Dividing))
Summary_CC_Div2
```

Stats 2nd neighb Analysis By Cluster
```{r}
SecNb_Stats_Cluster <-Master_D12_Cl  %>% 
group_by(Experiment, Cell_Type,Treatment, Replicate, Cluster_ID) %>%
summarise(Mean_NbDist = mean(Cell_2nd_Nb_Dist))
```

```{r}
WLR_Stats <- ddply(Master_D12_Cl, c("Cell_Type", "Treatment"), summarise, WLR_mean=mean(WLR))
```

Activated NOTCH statistics (non dividong only)
```{r}
aNOTCHStats <-Master_D12_Cl[Master_D12_Cl$Cell_Cycle == "G0/G1",]  %>% 
group_by(Img_N, Experiment, Cell_Type,Treatment, Replicate, NOTCH_Act) %>%
summarise(Counts = length(NOTCH_Act),
          STB_means = mean(STB_Index))%>%
mutate(Perc = Counts / sum(Counts)*100)

```
Calculate Statistics for JunctionINdex
```{r}
Summary_aNOTCH <- ddply(aNOTCHStats, c("Img_N","Experiment", "Replicate", "Cell_Type", "Treatment", "NOTCH_Act"), summarise,
               n= length(Perc),
               mean = mean(Perc),
               sd   = sd(Perc))
Summary_aNOTCH
```

```{r}
MeanSD_JI <- ddply(Master_D12_Cl, c("EXP_Cond"), summarise,
               N    = length(STB_Index),
               mean_JI = mean(STB_Index),
               sd_JI   = sd(STB_Index),
               se_JI   = sd_JI / sqrt(N))
MeanSD_JI


```



```{r}
JunClMean <- aggregate(Master[, 17:20], list(Master$CellType, Master$Treatment), mean)
JunClSD <- aggregate(Master[, 17:20], list(Master$CellType, Master$Treatment), sd)
JunClMean
JunClSD
JunClMeanLong <- gather(JunClMean, JunctType, Mean, Jun_Jag:Jun_Stb, factor_key=TRUE)
JunClSDLong <- gather(JunClSD, JunctType, SD, Jun_Jag:Jun_Stb, factor_key=TRUE)
```







ANOVA Cell Cycle
```{r}
StatsCellCy <- aov(Perc~Cell_Type*Treatment*Cell_Cycle, data = CellCycle_Stats)
CellCl_ANOVA<-TukeyHSD(StatsCellCy)
Cell_Cycle_ANOVA <- CellCl_ANOVA[["Cell_Type:Treatment:Cell_Cycle"]]
```



Stats summary for dividing cells
```{r}
library(reshape2)
S_Cell_Cy_Div <- dcast(Summary_CellCycle, Cell_Type + Treatment ~ Cell_Cycle, value.var="mean")
S_Cell_Cy_Div[is.na(S_Cell_Cy_Div)] <-0
S_Cell_Cy_SD <- dcast(Summary_CellCycle, Cell_Type + Treatment ~ Cell_Cycle, value.var="sd")
S_Cell_Cy_SD[is.na(S_Cell_Cy_SD)] <-0
S_Cell_Cy_Div$Dividing <- (S_Cell_Cy_Div$'G2/M'+S_Cell_Cy_Div$LM)
S_Cell_Cy_SD$Dividing_SD <- ((S_Cell_Cy_SD$'G2/M'+S_Cell_Cy_SD$LM)/2)
S_Cell_Cy_Div$Dividing_SD <- S_Cell_Cy_SD$Dividing_SD
S_Cell_Cy_SD
S_Cell_Cy_Div
```



ANOVA Cell Classes
```{r}
StatsCellClass <- aov(Perc~Cell_Type*Treatment*Cell_Act_Cl, data = CellAct_Stats)
CellClass_ANOVA<-TukeyHSD(StatsCellClass)
Cell_Class_ANOVA <- CellClass_ANOVA[["Cell_Type:Treatment:Cell_Act_Cl"]]
```

Stats JCyR
```{r}
JCyR_Stats <- Master_D12_Cl  %>% 
group_by(Experiment,Cell_Type,Treatment, Replicate, Img_N) %>%
summarise(Mean_JCyR = mean(JCyR),
          SD_JCyR = sd(JCyR))

Summary_JCyR <- ddply(JCyR_Stats, c("Cell_Type", "Treatment"), summarise,
               n = length(Mean_JCyR),
               mean = mean(Mean_JCyR),
               sd   = sd(SD_JCyR))
Summary_JCyR
JCyR_Stats
```