---
title: "R Service Notebook"
output: html_notebook
---
Load RSQlite library used to connect to db
```{r}
library(DBI)
library(RSQLite)
select <- dplyr::select
```

Extract DATA from Database
```{r}
SLAS2 <- dbConnect(RSQLite::SQLite(), "/Volumes/Lory Data 3 (APFS)/HCIAEC_2020/CPOutput/GlobalRun_110820.db")

Per_Cell <- tbl(SLAS2, "Per_Cell")
Per_Img <- tbl(SLAS2, "Per_Image")
Per_JA <- tbl(SLAS2, "Per_CellJunctArea")
Per_CO <- tbl(SLAS2, "Per_CellsObj")
Per_Nu <- tbl(SLAS2, "Per_Nuclei")
Per_Cy_NDts <- tbl(SLAS2, "Per_NDotsCy")
Per_Nu_NDts <- tbl(SLAS2, "Per_NDotsNu")
Cell_ActClasses <- tbl(SLAS2, "Cell_ActCl")

Cell_Act_Cl <-Cell_ActClasses%>%
  select (Cell_Act_Cl = class,
          Cell_Act_Cl_N = class_number)%>%
  collect()

Per_C_e_Im <- Per_Cell %>%
  left_join(Per_Img) %>%
 select (Img_N = ImageNumber,
         Img_Blur = Image_Blurred_Blur, 
         Experiment = Image_Metadata_Experiment,
         Experiment_N = Image_Group_Number,
         Img_Nuclei_N = Image_Count_Nuclei,
         Cell_Type = Image_Metadata_Cell,
         Treatment = Image_Metadata_Treatment,
         Replicate = Image_Metadata_Replicate,
         Well = Image_Metadata_Well,
         Cell_N = Cell_Number_Object_Number,
         Cell_VEC_MeanI = Cell_Intensity_MeanIntensity_VECOrig)%>%
  collect()

Per_CJA <-Per_JA%>%
  select (Junct_VEC_MeanI = CellJunctArea_Intensity_MeanIntensity_VECOrig)%>%
  collect()

Per_CObj <- Per_CO %>%
  select (Cell_NCheck = CellsObj_Number_Object_Number,
          Cell_Area = CellsObj_AreaShape_Area,
          Cell_Perim = CellsObj_AreaShape_Perimeter,
          Cell_MaxL = CellsObj_AreaShape_MajorAxisLength,
          Cell_MinL = CellsObj_AreaShape_MinorAxisLength,
          Cell_Orientation = CellsObj_AreaShape_Orientation,
          Cell_Neighbour_N = CellsObj_Neighbors_NumberOfNeighbors_Expanded,
          Cell_1st_Nb_Dist = CellsObj_Neighbors_FirstClosestDistance_Expanded,
          Cell_2nd_Nb_Dist = CellsObj_Neighbors_SecondClosestDistance_Expanded,
          Perc_Touch = )%>%
  collect()
Per_Junct <- Per_CO %>%
  select (Stb_J_N = CellsObj_Children_Stb_Count,
          Lin_J_N = CellsObj_Children_Lin_Count,
          Jag_J_N = CellsObj_Children_Jag_Count,
          NaJ_J_N = CellsObj_Children_NaJ_Count)%>%
  collect()
Per_Junct$J_N <- (Per_Junct$Stb_J_N+Per_Junct$Lin_J_N+Per_Junct$Jag_J_N)
Per_Junct$Perc_Stb <- (Per_Junct$Stb_J_N/Per_Junct$J_N*100)
Per_Junct$Perc_Lin <- (Per_Junct$Lin_J_N/Per_Junct$J_N*100)
Per_Junct$Perc_Jag <- (Per_Junct$Jag_J_N/Per_Junct$J_N*100)
Per_Junct$STB_Index <- (Per_Junct$Perc_Stb+ (0.5*Per_Junct$Perc_Lin)-Per_Junct$Perc_Jag)
Per_Junct$Stb_J_N <- NULL
Per_Junct$Lin_J_N <- NULL
Per_Junct$Jag_J_N <- NULL
Per_Junct$NaJ_J_N <- NULL

Per_Nuclei <- Per_Nu %>%
  select(Nu_X = Nuclei_Location_Center_X,
         Nu_Y = Nuclei_Location_Center_Y,
         DNA_IntI = Nuclei_Intensity_IntegratedIntensity_Nuclei,
         Nu_Clustering = Nuclei_Neighbors_NumberOfNeighbors_20,
         Nu_1st_Nb_Dist = Nuclei_Neighbors_FirstClosestDistance_20,
         Nu_2nd_Nb_Dist = Nuclei_Neighbors_SecondClosestDistance_20,
    Nu_Area = Nuclei_AreaShape_Area
    )%>%
collect()

Per_Cytoplasmic_NDts <- Per_Cy_NDts %>%
  select(Cy_NCH_IntI = NDotsCy_Intensity_IntegratedIntensity_NOTCH)%>%
  collect()
Per_Nuclei_NDts <- Per_Nu_NDts %>%
  select(Nu_NCH_IntI = NDotsNu_Intensity_IntegratedIntensity_NOTCH)%>%
  collect()

A_Master_D12 <- as_tibble(bind_cols(Per_C_e_Im,Per_CJA,Per_CObj, Cell_Act_Cl, Per_Nuclei,Per_Junct,Per_Cytoplasmic_NDts,Per_Nuclei_NDts))

#A_Master_D12$JCyR <- (A_Master_D12$Junct_VEC_MeanI/A_Master_D12$Cell_VEC_MeanI)

A_Master_D12 <- as_tibble(append(A_Master_D12,list(VEC_JCyR=(A_Master_D12$Junct_VEC_MeanI/A_Master_D12$Cell_VEC_MeanI)), after=8))
A_Master_D12 <- as_tibble(append(A_Master_D12,list(WLR=(A_Master_D12$Cell_MinL/A_Master_D12$Cell_MaxL)), after=13))

dbDisconnect(SLAS2)
rm(Cell_ActClasses,Per_C_e_Im,Per_CJA,Per_CObj,Per_Nuclei,Per_Junct,Per_Cytoplasmic_NDts,Per_Nuclei_NDts)
rm(Cell_Act_Cl,Per_Cell, Per_Img, Per_JA, Per_CO, Per_Nu, Per_Cy_NDts, Per_Nu_NDts)
```

```{r}
SLAS2 <- dbConnect(RSQLite::SQLite(), "/Volumes/Lory Data 3 (APFS)/HCIAEC_2020/CPOutput/GlobalRun_110820.db")

Per_Relation <- tbl(SLAS2, "Per_Relationships")

Neighbours_Id <- Per_Relation%>%
  select (Rel_Type = relationship_type_id, 
          Img_N = image_number1,
          Img_Neigh_N = image_number2,
          Cell_Id = object_number1,
          Neighbour_Id = object_number2)%>%
  collect()
Neighbours_Id <-Neighbours_Id[Neighbours_Id$Rel_Type == 4, ]
Neighbours_Id$Rel_Type <- NULL
Neighbours_Id$Img_Neigh_N <- NULL
A_Master_D12$Un_Cell_Id <- paste0(A_Master_D12$Img_N,"_", A_Master_D12$Cell_N)


dbDisconnect(SLAS2)
```

Turn NA into 0 (When there are no NOTCH dots CP export NA instead of 0)
```{r}
Master_D12$Cy_NCH_IntI <- ifelse(is.na(Master_D12$Cy_NCH_IntI) , 0, Master_D12$Cy_NCH_IntI)
Master_D12$Nu_NCH_IntI <- ifelse(is.na(Master_D12$Nu_NCH_IntI) , 0, Master_D12$Nu_NCH_IntI)
```

Dropping STB_Index=NA and Cell_Act_Cl= NC in dataframe (missegmented cels where junctions cannot be found and out of focus NC cells)
```{r}
Master_D12 <- drop_na(Master_D12, STB_Index)
Master_D12_Cl <- subset(Master_D12, Cell_Act_Cl != "NC")
```

_________________
Cleaning Database
_________________

D2R3 (without replicates embedded in names) Adding technical replicates column
```{r}
Master_D12_Cl$Replicate <- 
  ifelse(Master_D12_Cl$Experiment == "D1R3" & Master_D12_Cl$Well %in% c("B02","D02","F02","B06","D06","F06"), "1",
  ifelse(Master_D12_Cl$Experiment == "D1R3" & Master_D12_Cl$Well %in% c("B03","D03","F03","B07","D07","F07"), "2",
  ifelse(Master_D12_Cl$Experiment == "D1R3" & Master_D12_Cl$Well %in% c("B04","D04","F04","B08","D08","F08"), "3", Master_D12_Cl$Replicate)))

```

Stats for DNA Intensity Normalisation
```{r}
MeanSD_DNA <- ddply(Master_D12_Cl, c("Experiment", "Cell_Type", "Treatment"), summarise,
               N    = length(DNA_IntI),
               mean = mean(DNA_IntI),
               sd   = sd(DNA_IntI))
MeanSD_DNA

MeanSD_DNA$GlbMean <- mean(MeanSD_DNA$mean)
MeanSD_DNA$DNA_NormFact <- (MeanSD_DNA$GlbMean/MeanSD_DNA$mean)
MeanSD_DNA

Norm_Factor <- Master_D12_Cl %>%
  left_join(MeanSD_DNA) %>%
 select (NF = DNA_NormFact)%>%
  collect()
Master_D12_Cl$DNA_IntI_Norm <- (Master_D12_Cl$DNA_IntI*Norm_Factor$NF)
```
Assign Cell Cycle labels 
```{r}
Master_D12_Cl$Cell_Cycle <- ifelse(Master_D12_Cl$DNA_IntI_Norm <= 1300, "G0/G1", ifelse(Master_D12_Cl$DNA_IntI_Norm > 1300 & Master_D12_Cl$DNA_IntI_Norm <= 1600, "S","G2/M"))
Master_D12_Cl$Cell_Cycle <- ifelse(Master_D12_Cl$Cell_Act_Cl == "Dividing", "LM", Master_D12_Cl$Cell_Cycle)
```

VEC intensity normalisation
```{r}
MeanSD_VEC <- ddply(Master_D12_Cl, c("Experiment", "Cell_Type"), summarise,
               N    = length(Cell_VEC_MeanI),
               mean = mean(Cell_VEC_MeanI),
               sd   = sd(Cell_VEC_MeanI))
MeanSD_VEC

MeanSD_VEC$GlbMean <- mean(MeanSD_VEC$mean)
MeanSD_VEC$VEC_NormFact <- (MeanSD_VEC$GlbMean/MeanSD_VEC$mean)
MeanSD_VEC

Norm_Factor <- Master_D12_Cl %>%
  left_join(MeanSD_VEC) %>%
 select (NF = VEC_NormFact)%>%
  collect()
Master_D12_Cl$Cell_VEC_Norm <- (Master_D12_Cl$Cell_VEC_MeanI*Norm_Factor$NF)
Master_D12_Cl$Junc_VEC_Norm <- (Master_D12_Cl$Junct_VEC_MeanI*Norm_Factor$NF)
Master_D12_Cl$JCyR <- (Master_D12_Cl$Junc_VEC_Norm/Master_D12_Cl$Cell_VEC_Norm)
```

Dropping Cell_Area> 50000 and J_N <10 (unless LM) in dataframe (Out of focus, overlapping or partial cells which cannot be measured reliably)
```{r}
Master_D12_Cl <- subset(Master_D12_Cl, Cell_Area < 51000)
Master_D12_Cl <- subset(Master_D12_Cl, J_N > 10 | Cell_Cycle == "LM")
Master_D12_Cl <- subset(Master_D12_Cl, Nu_Area < 6000)
```

Compact and reorder database
```{r}
Master_D12_Cl <- Master_D12_Cl[,c("Img_N", "Experiment", "Img_Nuclei_N", "Cell_Type", "Treatment", "Replicate", "Well",
"Cell_N", "Un_Cell_Id", "Nu_X", "Nu_Y","Cell_Act_Cl", "Cell_Orientation", "Cell_Area", "Cell_Perim", "Cell_MaxL", "Cell_MinL", "WLR", "Cell_Neighbour_N", "Cell_1st_Nb_Dist", "Cell_2nd_Nb_Dist", "Nu_Clustering", "Nu_1st_Nb_Dist", "Nu_2nd_Nb_Dist", "Nu_Area", "DNA_IntI_Norm", "Cell_Cycle",
"Cell_VEC_Norm", "Junc_VEC_Norm", "JCyR", "J_N", "Perc_Stb", "Perc_Lin", "Perc_Jag", "STB_Index", 
"Cy_NCH_IntI", "Nu_NCH_IntI")]

```
________________________
NOTCH activation classes
```{r}
Master_D12_Cl$NOTCH_Act <- ifelse(Master_D12_Cl$Nu_NCH_IntI >50, "ON", ifelse(Master_D12_Cl$Tot_NCH > 50 & Master_D12_Cl$Nu_NCH_IntI <=50, "High",ifelse(Master_D12_Cl$Tot_NCH == 0, "OFF","Low")))

```
NOTCH Calculations
```{r}
Master_D12_Cl$Tot_NCH<- (Master_D12_Cl$Nu_NCH_IntI+Master_D12_Cl$Cy_NCH_IntI)

Master_D12_Cl$Nu_NOTCH_Fraction <- ifelse(Master_D12_Cl$Tot_NCH==0,-0.1,                                      ifelse(Master_D12_Cl$Cy_NCH_IntI==0 & Master_D12_Cl$Nu_NCH_IntI !=0, 1, (Master_D12_Cl$Nu_NCH_IntI/Master_D12_Cl$Tot_NCH)))
```

________________________
Dimensionality Reduction
________________________


PCA Intensities

```{r}
Master_D12_PCA <- Master_D12_Cl[,c(2,4,5,14:37)]
Master_D12_PCA$Cell_Cycle<-NULL

Master_D12_PCA_N <-normalize(Master_D12_PCA[,4:26], method = "range", range = c(0,1), margin = 1L, on.constant = "quiet")
Master_D12_PCA[,4:26]<-Master_D12_PCA_N

A_PCA_D12 <- prcomp(Master_D12_PCA[,4:26])
summary(A_PCA_D12)


```

```{r}
ggbiplot(A_PCA_D12, alpha = 0.5, scale = 1, ellipse = TRUE, varname.adjust = 2, ellipse.prob = 0.9, var.axes = TRUE, groups = Master_D12_PCA$Experiment)+lory_theme()

```


PCA Morph
```{r}
a_Morph_PCA <- Master_D12_Cl[,c("Cell_Area", "Cell_Perim", "Cell_MaxL", "Cell_MinL", "Nu_Area", "WLR")]
a_Morph_PCA <-normalize(a_Morph_PCA, method = "range", range = c(0,1), margin = 1L, on.constant = "quiet")
PCA_morph<-prcomp(a_Morph_PCA)
summary(PCA_morph)

```
PCA Intensities
```{r}
a_Int_PCA <- Master_D12_Cl[,c("Cell_VEC_Norm", "Junc_VEC_Norm", "Cy_NCH_IntI", "Nu_NCH_IntI", "DNA_IntI_Norm")]
a_Int_PCA <-normalize(a_Int_PCA, method = "range", range = c(0,1), margin = 1L, on.constant = "quiet")
PCA_Int<-prcomp(a_Int_PCA)
summary(PCA_Int)
```

PCA Neighborhood
```{r}
a_Neigh_PCA <- Master_D12_Cl[,c("Cell_Neighbour_N", "Cell_1st_Nb_Dist", "Cell_2nd_Nb_Dist", "Nu_Clustering", "Nu_1st_Nb_Dist", "Nu_2nd_Nb_Dist")]
a_Neigh_PCA <-normalize(a_Neigh_PCA, method = "range", range = c(0,1), margin = 1L, on.constant = "quiet")
PCA_Neigh<-prcomp(a_Neigh_PCA)
summary(PCA_Neigh)
```
PCA Junctions
```{r}
a_Jun_PCA <- Master_D12_Cl[,c("Perc_Stb", "Perc_Lin", "Perc_Jag", "JCyR", "STB_Index", "Junc_VEC_Norm")]
a_Jun_PCA <-normalize(a_Jun_PCA, method = "range", range = c(0,1), margin = 1L, on.constant = "quiet")
PCA_Jun<-prcomp(a_Jun_PCA)
summary(PCA_Jun)
```

PCAs for tSNE
```{r}
a_PCAs_tS <- cbind(PCA_Int$x[,1:3],PCA_Jun$x[,1:3], PCA_morph$x[,1:3], PCA_Neigh$x[,1:3])
```

```{r}
set.seed(42)
A_tSNE_cPCAs5x <- Rtsne(a_PCAs_tS, perplexity = 10, initial_dims = 12, max_iter = 1000, theta =0.5, pca=FALSE)
plot(A_tSNE_cPCAs5x$Y, col=factor(Master_D12_Cl$Cell_Type), xlab="tSNE1",ylab="tSNE2",cex=0.3)
```




Batch effect analysis
```{r}
Master_D12_PCA2 <- Master_D12_Cl
Master_D12_PCA2$Junct_VEC_MeanI<-Master_D12_PCA2$Cell_NCheck<-Master_D12_PCA2$Cell_Orientation<-Master_D12_PCA2$Cell_Act_Cl_N<-Master_D12_PCA2$Nu_X<-Master_D12_PCA2$Nu_Y<-Master_D12_PCA2$J_N<- Master_D12_PCA2$Perc_Stb<- Master_D12_PCA2$Perc_Lin<-Master_D12_PCA2$Perc_Jag<- Master_D12_PCA2$DNA_IntI_Norm<- Master_D12_PCA2$STB_Index<-Master_D12_PCA2$WLR<- Master_D12_PCA2$JCyR<- Master_D12_PCA2$Cell_MaxL<- Master_D12_PCA2$Cell_MinL<- Master_D12_PCA2$Cell_Area<- Master_D12_PCA2$Cell_Perim<-Master_D12_PCA2$Cell_Neighbour_N<-Master_D12_PCA2$Cell_1st_Nb_Dist<-Master_D12_PCA2$Cell_2nd_Nb_Dist<- Master_D12_PCA2$Nu_Clustering<- Master_D12_PCA2$Nu_1st_Nb_Dist<-Master_D12_PCA2$Nu_2nd_Nb_Dist<-Master_D12_PCA2$Nu_Area<- Master_D12_PCA2$Cell_VEC_MeanI<-NULL

Master_D12_PCA_N2 <-normalize(Master_D12_PCA2[,12:18], method = "range", range = c(0,1), margin = 1L, on.constant = "quiet")
Master_D12_PCA2[,12:18]<-Master_D12_PCA_N2

A_PCA2_D12 <- prcomp(Master_D12_PCA2[,c(12:14,17:18)])
summary(A_PCA2_D12)

```
Plot PCA2
```{r}
ggbiplot(A_PCA2_D12, alpha = 0.5, scale = 1, ellipse = TRUE, varname.adjust = 2, ellipse.prob = 0.69, var.axes = TRUE, groups = Master_D12_PCA2$Experiment)+lory_theme()

```


tSNE
```{r}
Master_D12_tSNE <- Master_D12_Cl[,c(1,3:10,13,15:18,20:22,36:38,41,43:44)]
Master_D12_tSNE$Cell_Cycle<- NULL
# Master_D12_tSNE$Cell_Type_N<-ifelse(Master_D12_tSNE$Cell_Type== "HAoEC", 1,                          ifelse(Master_D12_tSNE$Cell_Type=="HPMEC",2,3))
# Master_D12_tSNE$Treatment_N<-ifelse(Master_D12_tSNE$Treatment== "VEGF", 1,0)

Master_D12_tSNE_N <-normalize(Master_D12_tSNE[,10:23], method = "range", range = c(0,1), margin = 1L, on.constant = "quiet")
Master_D12_tSNE[,10:23]<-Master_D12_tSNE_N

```

```{r}
set.seed(42)
A_tSNE_D12_50_AllNoPCA_1000 <- Rtsne(Master_D12_tSNE_N, perplexity = 50, initial_dims = 15, max_iter = 1000, theta =0.1, pca=FALSE, num_threads=4)
plot(A_tSNE_D12_50_AllNoPCA_1000$Y, col=factor(Master_D12_Cl$Cell_Type), xlab="tSNE1",ylab="tSNE2",cex=0.3)

```

Assigning cluster ID to individual cells
```{r}
Master_D12_Cl$Cluster_ID <- ifelse(Master_D12_Cl$Un_Cell_Id %in% cluster_1$Un_Cell_Id , 1, ifelse(Master_D12_Cl$Un_Cell_Id %in% cluster_2$Un_Cell_Id,2, ifelse(Master_D12_Cl$Un_Cell_Id %in% cluster_3$Un_Cell_Id,3,ifelse(Master_D12_Cl$Un_Cell_Id %in% cluster_4$Un_Cell_Id,4,ifelse(Master_D12_Cl$Un_Cell_Id %in% cluster_5$Un_Cell_Id,5,ifelse(Master_D12_Cl$Un_Cell_Id %in% cluster_6$Un_Cell_Id,6,0))))))
```

_________
Functions
_________

```{r}
#  
#  Copyright 2011 Vincent Q. Vu.
# 
#  This program is free software; you can redistribute it and/or
#  modify it under the terms of the GNU General Public License
#  as published by the Free Software Foundation; either version 2
#  of the License, or (at your option) any later version.
#  
#  This program is distributed in the hope that it will be useful,
#  but WITHOUT ANY WARRANTY; without even the implied warranty of
#  MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
#  GNU General Public License for more details.
#  
#  You should have received a copy of the GNU General Public License
#  along with this program; if not, write to the Free Software
#  Foundation, Inc., 51 Franklin Street, Fifth Floor, Boston, MA  02110-1301, USA.
# 

#' Biplot for Principal Components using ggplot2
#'
#' @param pcobj           an object returned by prcomp() or princomp()
#' @param choices         which PCs to plot
#' @param scale           covariance biplot (scale = 1), form biplot (scale = 0). When scale = 1, the inner product between the variables approximates the covariance and the distance between the points approximates the Mahalanobis distance.
#' @param obs.scale       scale factor to apply to observations
#' @param var.scale       scale factor to apply to variables
#' @param pc.biplot       for compatibility with biplot.princomp()
#' @param groups          optional factor variable indicating the groups that the observations belong to. If provided the points will be colored according to groups
#' @param ellipse         draw a normal data ellipse for each group?
#' @param ellipse.prob    size of the ellipse in Normal probability
#' @param labels          optional vector of labels for the observations
#' @param labels.size     size of the text used for the labels
#' @param alpha           alpha transparency value for the points (0 = transparent, 1 = opaque)
#' @param circle          draw a correlation circle? (only applies when prcomp was called with scale = TRUE and when var.scale = 1)
#' @param var.axes        draw arrows for the variables?
#' @param varname.size    size of the text for variable names
#' @param varname.adjust  adjustment factor the placement of the variable names, >= 1 means farther from the arrow
#' @param varname.abbrev  whether or not to abbreviate the variable names
#'
#' @return                a ggplot2 plot
#' @export
#' @examples
#'   data(wine)
#'   wine.pca <- prcomp(wine, scale. = TRUE)
#'   print(ggbiplot(wine.pca, obs.scale = 1, var.scale = 1, groups = wine.class, ellipse = TRUE, circle = TRUE))
#'
ggbiplot <- function(pcobj, choices = 1:2, scale = 1, pc.biplot = TRUE, 
                      obs.scale = 1 - scale, var.scale = scale, 
                      groups = NULL, ellipse = FALSE, ellipse.prob = 0.68, 
                      labels = NULL, labels.size = 3, alpha = 1, 
                      var.axes = TRUE, 
                      circle = FALSE, circle.prob = 0.69, 
                      varname.size = 3, varname.adjust = 1.5, 
                      varname.abbrev = FALSE, ...)
{
  library(ggplot2)
  library(plyr)
  library(scales)
  library(grid)

  stopifnot(length(choices) == 2)

  # Recover the SVD
 if(inherits(pcobj, 'prcomp')){
    nobs.factor <- sqrt(nrow(pcobj$x) - 1)
    d <- pcobj$sdev
    u <- sweep(pcobj$x, 2, 1 / (d * nobs.factor), FUN = '*')
    v <- pcobj$rotation
  } else if(inherits(pcobj, 'princomp')) {
    nobs.factor <- sqrt(pcobj$n.obs)
    d <- pcobj$sdev
    u <- sweep(pcobj$scores, 2, 1 / (d * nobs.factor), FUN = '*')
    v <- pcobj$loadings
  } else if(inherits(pcobj, 'PCA')) {
    nobs.factor <- sqrt(nrow(pcobj$call$X))
    d <- unlist(sqrt(pcobj$eig)[1])
    u <- sweep(pcobj$ind$coord, 2, 1 / (d * nobs.factor), FUN = '*')
    v <- sweep(pcobj$var$coord,2,sqrt(pcobj$eig[1:ncol(pcobj$var$coord),1]),FUN="/")
  } else if(inherits(pcobj, "lda")) {
      nobs.factor <- sqrt(pcobj$N)
      d <- pcobj$svd
      u <- predict(pcobj)$x/nobs.factor
      v <- pcobj$scaling
      d.total <- sum(d^2)
  } else {
    stop('Expected a object of class prcomp, princomp, PCA, or lda')
  }

  # Scores
  choices <- pmin(choices, ncol(u))
  df.u <- as.data.frame(sweep(u[,choices], 2, d[choices]^obs.scale, FUN='*'))

  # Directions
  v <- sweep(v, 2, d^var.scale, FUN='*')
  df.v <- as.data.frame(v[, choices])

  names(df.u) <- c('xvar', 'yvar')
  names(df.v) <- names(df.u)

  if(pc.biplot) {
    df.u <- df.u * nobs.factor
  }

  # Scale the radius of the correlation circle so that it corresponds to 
  # a data ellipse for the standardized PC scores
  r <- sqrt(qchisq(circle.prob, df = 2)) * prod(colMeans(df.u^2))^(1/4)

  # Scale directions
  v.scale <- rowSums(v^2)
  df.v <- r * df.v / sqrt(max(v.scale))

  # Change the labels for the axes
  if(obs.scale == 0) {
    u.axis.labs <- paste('standardized PC', choices, sep='')
  } else {
    u.axis.labs <- paste('PC', choices, sep='')
  }

  # Append the proportion of explained variance to the axis labels
  u.axis.labs <- paste(u.axis.labs, 
                       sprintf('(%0.1f%% explained var.)', 
                               100 * pcobj$sdev[choices]^2/sum(pcobj$sdev^2)))

  # Score Labels
  if(!is.null(labels)) {
    df.u$labels <- labels
  }

  # Grouping variable
  if(!is.null(groups)) {
    df.u$groups <- groups
  }

  # Variable Names
  if(varname.abbrev) {
    df.v$varname <- abbreviate(rownames(v))
  } else {
    df.v$varname <- rownames(v)
  }

  # Variables for text label placement
  df.v$angle <- with(df.v, (180/pi) * atan(yvar / xvar))
  df.v$hjust = with(df.v, (1 - varname.adjust * sign(xvar)) / 2)

  # Base plot
  g <- ggplot(data = df.u, aes(x = xvar, y = yvar)) + 
          xlab(u.axis.labs[1]) + ylab(u.axis.labs[2]) + coord_equal()

  if(var.axes) {
    # Draw circle
    if(circle) 
    {
      theta <- c(seq(-pi, pi, length = 50), seq(pi, -pi, length = 50))
      circle <- data.frame(xvar = r * cos(theta), yvar = r * sin(theta))
      g <- g + geom_path(data = circle, color = muted('white'), 
                         size = 1/2, alpha = 1/3)
    }

    
  }

  # Draw either labels or points
  if(!is.null(df.u$labels)) {
    if(!is.null(df.u$groups)) {
      g <- g + geom_text(aes(label = labels, color = groups), 
                         size = labels.size)
    } else {
      g <- g + geom_text(aes(label = labels), size = labels.size)      
    }
  } else {
    if(!is.null(df.u$groups)) {
      g <- g + geom_point(aes(color = groups),size = 0.05, shape = 16, alpha = alpha)
    } else {
      g <- g + geom_point(alpha = alpha)      
    }
  }

  # Overlay a concentration ellipse if there are groups
  if(!is.null(df.u$groups) && ellipse) {
    theta <- c(seq(-pi, pi, length = 50), seq(pi, -pi, length = 50))
    circle <- cbind(cos(theta), sin(theta))

    ell <- ddply(df.u, 'groups', function(x) {
      if(nrow(x) <= 2) {
        return(NULL)
      }
      sigma <- var(cbind(x$xvar, x$yvar))
      mu <- c(mean(x$xvar), mean(x$yvar))
      ed <- sqrt(qchisq(ellipse.prob, df = 2))
      data.frame(sweep(circle %*% chol(sigma) * ed, 2, mu, FUN = '+'), 
                 groups = x$groups[1])
    })
    names(ell)[1:2] <- c('xvar', 'yvar')
    g <- g + geom_path(data = ell, aes(color = groups, group = groups))
  }

  # Label the variable axes
  if(var.axes) {
    g <- g + 
    geom_text(data = df.v, 
              aes(label = varname, x = xvar, y = yvar, 
                  angle = angle, hjust = hjust), 
              color = 'darkred', size = varname.size)
  }
 # Draw directions
    g <- g +
      geom_segment(data = df.v,
                   aes(x = 0, y = 0, xend = xvar, yend = yvar),
                   arrow = arrow(length = unit(1/2, 'picas')), 
                   color = muted('red'))
   # Change the name of the legend for groups
  # if(!is.null(groups)) {
  #   g <- g + scale_color_brewer(name = deparse(substitute(groups)), 
  #                               palette = 'Dark2')
  # }

  # TODO: Add a second set of axes

  return(g)
}
```
