---
title: "ECPT-Plots"
output:
  html_notebook: 
  word_document: 
  pdf_document:
  html_document:
    df_print: paged
---
Packages used in the project
___________________________________________________________
Can change each element in following list with 
<if (!requireNamespace("Package", quietly = TRUE))
install.packages("Package")> 
to check if package is already installed before attempting installation.
___________________________________________________________
```{r}
install.packages("plyr")
install.packages("ggplot2")
install.packages("plotly")
install.packages("corrr")
install.packages("ggstance")
install.packages("ggpubr")
install.packages("devtools")
install.packages("remotes")
devtools::install_github("hadley/plyr")
install.packages("BiocManager")
BiocManager::install("sva")
install.packages("Rtsne")
install.packages("umap")
install.packages("gatepoints")
install.packages("caret")
install.packages("e1071")
```

Import Libraries
```{r}
library(plyr)
library(dplyr)
library(corrr)
library(plotly)
library(ggplot2)
library(ggstance)
library(car)
library(MASS)
library(tidyverse)
library(scales)
library(viridis)
library(ggpmisc) 
library(tidyr)
library(RColorBrewer)
library(ggpubr)
library(devtools)
library(BBmisc)
library(Rtsne)
library(data.table)
library(gatepoints)
library(caret)
library(e1071)
```
________________________________________________________

This is the Graphic theme used throughout the project
```{r}
ECPT_theme <- function() {
  theme(
    plot.background = element_rect(colour = "transparent", fill = "transparent"),
    # add border 1)
    
    strip.background = element_rect(colour="transparent", fill = "transparent"),
    strip.text = element_text(family = "Arial", colour = "transparent", size = 8),
    strip.placement = "inside",
    panel.border = element_rect(colour = "grey25", fill = NA, linetype = 1),
    # color background 2)

    panel.background = element_rect(fill = "white"),
    # modify grid 3)
    panel.grid.major.x = element_line(colour = "grey25", linetype = 3, size = 0.15),
    panel.grid.minor.x = element_line(colour = "grey25", linetype = 3, size = 0.05),
    panel.grid.major.y =  element_line(colour = "grey25", linetype = 3, size = 0.15),
    panel.grid.minor.y = element_line(colour = "grey25", linetype = 3, size = 0.05),
    # modify text, axis and colour 4) and 5)
    
    axis.text = element_text(colour = "black", family = "Arial"),
    axis.title = element_text(colour = "black", family = "Arial"),
    axis.ticks = element_line(colour = "black"),
    # legend at the bottom 6)
    legend.position = "bottom"
  )
}
```
________________________________________________________

DNA peaks Plot
```{r}
Plot_DNApeaks <- ggplot(Master_D12_Cl, 
               aes(DNA_IntI_Norm, 
                   fill = factor(Experiment)))
Plot_DNApeaks+ 
geom_histogram(bins= 200, colour="transparent")+
ECPT_theme()+
#scale_color_brewer(palette = "Dark2")+
scale_fill_brewer(palette = "Dark2")+
scale_x_continuous(limits = c(550,3500), trans = "log10", breaks = c(1300, 1600))+
xlab("DNA intensity")+ 
facet_wrap(vars(Treatment, Cell_Type))
```
________________________________________________________

Cell Act Classes Crossbars By Cell Cycle Category with stats
```{r}
Plot_CellActCl_Box <- ggboxplot(CellAct_Stats, x = "Cell_Type", y = "Perc", color = "Cell_Type", palette = "Dark2", add = "jitter", shape= 16, size = 0.1, facet.by = c("Cell_Act_Cl", "Treatment"))

comparisons <- list(c("HAoEC", "HPMEC"), c("HAoEC", "HUVEC"), c("HPMEC", "HUVEC"))

Plot_CellActCl_Box+
ECPT_theme()+
scale_color_brewer(palette = "Dark2")+
scale_fill_brewer(palette = "Dark2")+
xlab("Cell Type")+
ylab("%")+
stat_compare_means(aes(label = ..p.signif..), comparisons = comparisons, label.y = c(25,45,65), tip.length = 0)

Plot_CellActCl_Box2 <- ggboxplot(CellAct_Stats, x = "Treatment", y = "Perc", color = "Cell_Type", palette = "Dark2", add = "jitter", shape= 16, size = 0.1, facet.by = c("Cell_Act_Cl", "Cell_Type"))

comparisons <- list(c("CTRL", "VEGF"))

Plot_CellActCl_Box2+
ECPT_theme()+
scale_color_brewer(palette = "Dark2")+
scale_fill_brewer(palette = "Dark2")+
xlab("Treatment")+
ylab("%")+
stat_compare_means(aes(label = ..p.signif..), comparisons = comparisons, label.y = c(25,45,65), tip.length = 0)
rm(Plot_CellActCl_Box)
rm(Plot_CellActCl_Box2)
rm(comparisons)
```

Stacked barplot Cell Cycle
```{r}
CellCyFactors <- factor(Master_D12_Cl$Cell_Cycle, levels = c("LM", "G2/M", "S","G0/G1"))

CCyStackBar <- ggplot(Master_D12_Cl, aes(x = Cell_Type, y=1, fill = CellCyFactors))+
geom_bar(stat="identity", position = "fill", show.legend = TRUE)+
scale_fill_manual(values = c("red","orange","yellow","darkgreen"))+
#scale_color_brewer(palette = "Dark2")+
#scale_fill_brewer(palette = "Dark2")+
ECPT_theme()+
facet_wrap(vars(Treatment))+
xlab("Cell Type")+
ylab(NULL)

CCyStackBar
```


Cell Cycle Crossbars By Cell Cycle Category with stats
```{r}
Plot_Cell_Cy_Box2 <- ggboxplot(CellCycle_Stats, x = "Cell_Type", y = "Perc", color = "Cell_Type", palette = "Dark2", add = "jitter", shape= 16, size = 0.1, facet.by = c("Cell_Cycle", "Treatment"))

comparisons <- list(c("HAoEC", "HPMEC"), c("HAoEC", "HUVEC"), c("HPMEC", "HUVEC"))

Plot_Cell_Cy_Box2+
ECPT_theme()+
scale_color_brewer(palette = "Dark2")+
scale_fill_brewer(palette = "Dark2")+
xlab("Cell Type")+
ylab("%")+
stat_compare_means(aes(label = ..p.signif..), comparisons = comparisons, label.y = c(25,45,65), tip.length = 0)

Plot_Cell_Cy_Box3 <- ggboxplot(CellCycle_Stats, x = "Treatment", y = "Perc", color = "Cell_Type", palette = "Dark2", add = "jitter", shape= 16, size = 0.1, facet.by = c("Cell_Cycle", "Cell_Type"))

comparisons <- list(c("CTRL", "VEGF"))

Plot_Cell_Cy_Box3+
ECPT_theme()+
scale_color_brewer(palette = "Dark2")+
scale_fill_brewer(palette = "Dark2")+
xlab("Treatment")+
ylab("%")+
stat_compare_means(aes(label = ..p.signif..), comparisons = comparisons, label.y = c(25,45,65), tip.length = 0)
rm(Plot_Cell_Cy_Box2)
rm(Plot_Cell_Cy_Box3)
rm(comparisons)
```


Cluster enrichment
```{r}
meansCCCl <- aggregate(Perc~Cluster_ID*Treatment*Cell_Cycle, data = CellCycle_Stats_Cluster[CellCycle_Stats_Cluster$Cluster_ID!=0,], mean)
meansCCCl$Perc<- round(meansCCCl$Perc, digits = 2)

Plot_Cell_Cy_Box2 <- ggboxplot(CellCycle_Stats_Cluster[CellCycle_Stats_Cluster$Cluster_ID!=0 & CellCycle_Stats_Cluster$Cell_Cycle=="G2/M",], x = "Cluster_ID", y = "Perc", color = "Cluster_ID", palette = "Dark2",add = "jitter", add.params = list(shape = 1, size = 0.3), shape= 16, size = 0.5, width = 0.5, line.size = 5,facet.by = c("Cell_Type"))

comparisons <- list(c("1", "2"), c("2", "3"), c("2", "4"),c("2", "5"),c("2", "6"))

Plot_Cell_Cy_Box2+
xlab("Cluster")+
ylab("% G2/M in cluster")+
scale_color_manual(values = c("red","purple","blue", "turquoise","green","darkgreen"))+
# geom_text(data = meansCCCl[meansCCCl$Cell_Cycle=="LM",], aes(label = Perc, y = 80))
# stat_compare_means(aes(label = ..p.signif..), comparisons = comparisons, tip.length = 0)
ECPT_theme()

Plot_Cell_Cy_Box3 <- ggboxplot(CellCycle_Stats_Cluster[CellCycle_Stats_Cluster$Cluster_ID!=0& CellCycle_Stats_Cluster$Cell_Cycle=="LM",], x = "Cluster_ID", y = "Perc", color = "Cluster_ID", palette = "Dark2", add = "jitter", shape= 16, size = 0.1, facet.by = c("Cell_Cycle", "Cell_Type"))


# comparisons <- list(c("1", "2"), c("1", "3"), c("1", "4"),c("1", "5"),c("1", "6"),c("2", "3"),c("2", "4"),c("2", "5"),c("2", "6"))

Plot_Cell_Cy_Box3+
ECPT_theme()+
scale_color_brewer(palette = "Dark2")+
scale_fill_brewer(palette = "Dark2")+
xlab("Cell Type")+
ylab("% LM in cluster")+
geom_text(data = meansCCCl[meansCCCl$Cell_Cycle=="LM",], aes(label = Perc, y = 80))
#stat_compare_means(aes(label = ..p.signif..), comparisons = comparisons, tip.length = 0)
rm(Plot_Cell_Cy_Box2)
rm(Plot_Cell_Cy_Box3)
rm(comparisons)
```
Cell Cycle In  Colonies SV sparse
```{r}
meansCCClCol <- aggregate(Counts~Colony*Cell_Type*Treatment*Cell_Cycle, data = CellCycle_Stats_Colony, mean)
meansCCClCol$Counts<- round(meansCCClCol$Counts, digits = 2)

Plot_Cell_Cy_Box2 <- ggboxplot(CellCycle_Stats_Colony[CellCycle_Stats_Colony$Cell_Cycle =="LM",], x = "Colony", y = "Counts", color = "black", palette = "Dark2",add = c("mean"), add.params = list(shape = 16, size = 0.3, color="red"), shape= 16, size = 0.5, width = 0.5, line.size = 5,facet.by = c("Treatment", "Cell_Type"))

# comparisons <- list(c("IC", "NIC"))

Plot_Cell_Cy_Box2+
xlab("Cluster")+
ylab("Average LM number/well")+
geom_text(data = meansCCClCol[meansCCClCol$Cell_Cycle=="LM",], aes(label = Counts, y = 120))+
# stat_compare_means(aes(label = ..p.signif..), comparisons = comparisons, tip.length = 0)+
ECPT_theme()
```
Cell Cycle boxplots by dividing with stats (including Per_Image Number)
```{r}
meansCC <- aggregate(Dividing~Cell_Type*Treatment, data = S_Cell_Cy_Div2, mean)
meansCC$Dividing<- round(meansCC$Dividing, digits = 2)

Plot_Cell_Cy_Box4 <- ggboxplot(S_Cell_Cy_Div2, x = "Cell_Type", y = "Dividing", color = "Cell_Type", add = "jitter", add.params = list(shape = 1, size = 0.3), shape= 16, size = 0.5, width = 0.5, line.size = 5, facet.by = c("Cell_Type"))

comparisons <- list(c("CTRL", "VEGF"))
comparisonsCT<- list(c("HAoEC", "HPMEC"),c("HAoEC", "HUVEC"),c("HUVEC", "HPMEC"))
Plot_Cell_Cy_Box4+
ECPT_theme()+
scale_color_manual(values = c("red", "green", "blue"))+
#scale_color_continuous(type = "viridis")+
# scale_fill_brewer(palette = "Dark2")+
xlab("Treatment")+
ylab("% Dividing Cells")+
#stat_compare_means(aes(label = ..p.signif..),comparisons = comparisonsCT, label.y = c(30,40,50), tip.length = 0)+
#geom_text(data = meansCC, aes(label = Dividing, y = c(35,45,55,35,45,55)))+

# Plot_CC_Dens <- ggplot(S_Cell_Cy_Div2)+
#   geom_violin(aes(Treatment, Dividing), draw_quantiles = c(0.25, 0.5, 0.75))
# 
# Plot_CC_Dens+ ECPT_theme() + 
facet_wrap(vars(Treatment))

# rm(Plot_Cell_Cy_Box4)
# rm(comparisons)
```
2nd Neighbour boxplots by cluster with stats
```{r}
meansNbDist <- aggregate(Mean_NbDist~Cluster_ID, data = SecNb_Stats_Cluster, mean)
meansNbDist$Mean_NbDist<- round(meansNbDist$Mean_NbDist, digits = 2)

Plot_Nb_Dist_Box <- ggboxplot(SecNb_Stats_Cluster[SecNb_Stats_Cluster$Cluster_ID!="0",], x = "Cluster_ID", y = "Mean_NbDist", color = "Cluster_ID", add = "jitter", add.params = list(shape = 1, size = 0.3), shape= 16, size = 0.5, width = 0.5, line.size = 5)

comparisons<- list(c("4", "3"),c("4", "6"),c("5", "3"), c("5", "6"))
Plot_Nb_Dist_Box+
xlab("Cluster")+
ylab("Mean 2nd Nb Distance")+
scale_color_manual(values = c("red","purple","blue", "turquoise","green","darkgreen"))+
stat_compare_means(aes(label = ..p.signif..),comparisons = comparisons, tip.length = 0)+
geom_text(data = meansNbDist[meansNbDist$Cluster_ID!="0",], aes(label = sd(Mean_NbDist)))+
ECPT_theme()

```
________________________________________________________
Area Plot
```{r}
Area <- ggplot(Master_D12_Cl, 
                  aes(Cell_Area)) 

Area + ECPT_theme()+
scale_x_continuous(limits = c(900,50000), trans = "identity")+
xlab("Cell Area")+ 
geom_histogram(bins = 100, aes(y = after_stat(count)))+
facet_wrap(vars(Treatment,Cell_Type))
```
________________________________________________________

Width/Length Ratio Plot
```{r}
WLR <- ggplot(Master_D12_Cl, 
                  aes(WLR, colour = factor(Treatment)))

WLR+
geom_density()+
stat_boxploth(aes(y= -0.1), width=0.2, size=0.2)+
geom_x_margin_point(data = WLR_Stats, aes(xintercept = WLR_mean, fill = factor(Treatment)))+

ECPT_theme()+
scale_color_manual(values = c("black","red"))+
scale_fill_manual(values = c("black","red"))+
scale_x_continuous(limits = c(0,1))+
xlab("Width/Length Ratio")+
facet_wrap(vars(Cell_Type))
```

________________________________________________________

VEC Intensity Plots
```{r}
mu <- ddply(Master_D12_Cl, c("Cell_Type", "Treatment"), summarise, VEC_mean=mean(Cell_VEC_Norm))

Vec_Intensity <- ggplot(Master_D12_Cl[(Master_D12_Cl$Cell_Cycle != "LM"),],aes(Cell_VEC_Norm, 
                      colour = factor(Cell_Type)))
Vec_Intensity+ 
geom_density() +
stat_boxploth(aes(y= -0.9), width=0.8, size=0.2)+
# geom_x_margin_point(data = mu, aes(xintercept = VEC_mean, fill = factor(Treatment)))+
scale_color_brewer(palette = "Dark2")+
scale_fill_brewer(palette = "Dark2")+
  ECPT_theme()+
  scale_x_continuous(limits = c(0,0.55)) +
  xlab("VEC Intensity") +
  facet_wrap(vars(Treatment))
```

J STB Index distribution Plots
```{r}
Plot_J_Index <- ggplot(Master_D12_Cl, 
                  aes(STB_Index, 
                      colour = factor(Treatment)))
Plot_J_Index+ 
#geom_histogram(bins = 6, position = "dodge", colour = "transparent") +
geom_density()+
#geom_density()+
stat_boxploth(aes(y= -0.002), width=0.002)+
# geom_x_margin_point(data = mu, aes(xintercept = VEC_mean, fill = factor(Treatment)))+
scale_color_manual(values = c("black","red"))+
#scale_color_brewer(palette = "Dark2")+
#scale_fill_brewer(palette = "Dark2")+
ECPT_theme()  +
scale_x_continuous(limits = c(-100,100)) +
xlab("Junctional Index")+
facet_wrap(vars(Cell_Type))
```

________________________________________________________

NOTCH PLot alternative
```{r}
aNOTCHCy_Nu <- ggplot(Master_D12_Cl)

aNOTCHCy_Nu+
geom_point(size= 0.7, shape = 16, aes(Tot_NCH,Nu_NCH_IntI, 
               colour = factor(NOTCH_Act)))+

# stat_function(data = data.frame(x = c(0.01,1)), mapping = aes(x) , fun = function(x) fun.1(x), colour = "red", size= 2)+
# stat_function(data = data.frame(x = c(0.01,1)), mapping = aes(x) , fun = function(x) fun.2(x), colour = "green", size=2)+
# stat_function(data = data.frame(x = c(0.01,1)), mapping = aes(x) , fun = function(x) fun.3(x), colour = "blue", size=2)+

#scale_color_gradient2 (midpoint=0, low="red", mid="orange",high="green", space ="Lab" )+
# geom_quadrant_lines(colour = "red",
#                     xintercept = 100,
#                     yintercept = 60)+
scale_y_continuous(limits = c(0, 4000),
                     breaks = c(0,50, 200,800, 1600),
                     trans = "log1p") +
scale_x_continuous(limits = c(0,4000),
                     breaks = c(0,50, 200,800,1600),
                     trans = "log1p") +
  
#scale_color_gradient2 (midpoint=0, low="red", mid="orange",                     high="green", space ="Lab" )+
scale_color_manual(values = c("orange","green", "darkgreen", "red"))+
#facet_wrap(vars(Treatment, Cell_Type))+
xlab("Total NICD Intensity") +
ylab("Nuclear NICD Intensity")+
ECPT_theme()
#aNOTCHCy_Nu
```

NICD Nuclear fraction Plots
```{r}
Plot_NCH_Dens<- ggplot(Master_D12_Cl[(Master_D12_Cl$Cell_Cycle != "LM"),],aes(Nu_NOTCH_Fraction, colour = factor(Treatment)))
Plot_NCH_Dens+ 
geom_freqpoly(binwidth = 0.005)+
#stat_boxploth(aes(y= -0.9), width=0.8, size=0.2)+
# geom_x_margin_point(data = mu, aes(xintercept = VEC_mean, fill = factor(Treatment)))+
# scale_color_brewer(palette = "Dark2")+
# scale_fill_brewer(palette = "Dark2")+
scale_color_manual(values=c("black","red","blue","black"))+  
  
  scale_x_continuous(limits = c(-0.2,1.1), breaks = c(0,0.5,1)) +
  scale_y_continuous(trans = "log1p", breaks = c(0,1000,10000))+
  xlab("Nuclear Fraction")+
facet_wrap(vars(Cell_Type))+
ECPT_theme()
```

```{r}
Plot_NCHCat_STB <- ggplot(Master_D12_Cl)

Plot_NCHCat_STB +
  geom_point(aes(NOTCH_Act, STB_Index), position = "jitter", size=0.1)+
  geom_boxplot(aes(NOTCH_Act, STB_Index), fill="transparent", colour = "red")+
  facet_wrap(vars(Treatment, Cell_Type))+
  ECPT_theme()
```

Stacked barplot NOTCH activation (With reordered factors)
```{r}
Factors <- factor(Master_D12_Cl$NOTCH_Act, levels = c("ON", "High","Low","OFF"))

QuadsStackBarPlot <- ggplot(Master_D12_Cl)+
  geom_bar(aes(x = Cell_Type, y=1, fill = Factors),stat="identity", position = "fill", show.legend = TRUE)+
facet_wrap(vars(Treatment))

QuadsStackBarPlot+
ECPT_theme()+
#scale_color_brewer(palette = "Dark2")+
#scale_fill_brewer(palette = "Dark2")+
scale_fill_manual(values = c("red","orange","blue","darkgreen"))+
xlab("Cell Type")+
ylab(NULL)

rm(Factors)
rm(QuadsStackBarPlot)
```

aNOTCH Crossbars By Quadrant Categories with stats
```{r}
Summary_aNOTCH$NOTCH_Act <- factor(Summary_aNOTCH$NOTCH_Act, levels = c("ON", "High","Low","OFF"))
Summary_aNOTCH$Cell_Type<- factor(Summary_aNOTCH$Cell_Type, levels = c("HAoEC", "HPMEC", "HUVEC"))
means <- aggregate(mean~Cell_Type*Treatment*NOTCH_Act, data = Summary_aNOTCH, mean)
means$mean<- round(means$mean, digits = 2)

ggscatter(data = aNOTCHStats[aNOTCHStats$NOTCH_Act == "Low",], x= "Perc", y= "STB_means",colour = "black", add = "reg.line",add.params = list(color = "red", fill = "lightgray"),    conf.int = TRUE)+ 

stat_cor(aes(Perc, STB_means, colour = "red"),method = "pearson", label.x = 3, label.y = c(80,90,100), p.accuracy = 0.001, r.accuracy = 0.01)+

xlab("Percent low cell/field")+
ylab("Mean Junctional Stability index/Field")+
ECPT_theme()
```

```{r}
Plot_aNOTCH_Box2 <- ggboxplot(Summary_aNOTCH, x = "Cell_Type", y = "mean", color = "Cell_Type", palette = "Dark2", add = "jitter", shape= 16, size = 0.1, facet.by = c("Treatment","NOTCH_Act"))+
geom_text(data = means, aes(label = mean, y = 98))

comparisons <- list(c("HAoEC", "HPMEC"), c("HAoEC", "HUVEC"), c("HPMEC", "HUVEC"))

Plot_aNOTCH_Box2+
ECPT_theme()+
scale_y_continuous(limits = c(0,100), breaks = c(10,20,40,60,80))+
scale_color_brewer(palette = "Dark2")+
scale_fill_brewer(palette = "Dark2")+
xlab("Cell Type")+
ylab("% cells in quadrant")+
stat_compare_means(aes(label = ..p.signif..), comparisons = comparisons, label.y = c(25), tip.length = 0)

Plot_aNOTCH_Box3 <- ggboxplot(Summary_aNOTCH, x = "Treatment", y = "mean", color = "Cell_Type", palette = "Dark2", add = "jitter", shape= 16, size = 0.5, facet.by = c("Cell_Type","NOTCH_Act"))+
geom_text(data = means, aes(label = mean, y = 25))

comparisons1 <- list(c("CTRL", "VEGF"))

Plot_aNOTCH_Box3+
ECPT_theme()+
scale_y_continuous(limits = c(0,100), breaks = c(0,50,100))+
scale_color_brewer(palette = "Dark2")+
scale_fill_brewer(palette = "Dark2")+
xlab("Treatment")+
ylab("%")+
stat_compare_means(aes(label = ..p.signif..), comparisons = comparisons1, label.y = c(85), tip.length = 0)
rm(Plot_aNOTCH_Box2)
rm(Plot_aNOTCH_Box3)
rm(comparisons)
rm(comparisons1)
```

_________________________________________________________________


Cell Act ClassesStacked Bars
```{r}
Factors <- factor(Master_D12_Cl$Cell_Act_Cl, levels = c("Dividing", "Stressed", "Activated","Quiescent"))

JunctStackBarPlot <- ggplot(Master_D12_Cl, aes(x = Cell_Type, y=1, fill =Factors))+
  geom_bar(stat="identity", position = "fill")+
scale_color_brewer(palette = "Dark2")+
scale_fill_brewer(palette = "Dark2")+
scale_fill_manual(values = c("grey","red","yellow","darkgreen"))+
facet_wrap(vars(Treatment))+
ECPT_theme()
JunctStackBarPlot
```


```{r}
Plot_STB_Density <- ggplot(Master_D12_Cl)
Plot_STB_Density + geom_density(aes(STB_Index, colour= factor(Cell_Type)))+
ECPT_theme()+
facet_wrap(vars(Treatment))
```


```{r}
# Master_D12_Cl$tSNE_1 <-A_tSNE_cPCAs5$Y[,1]
# Master_D12_Cl$tSNE_2 <-A_tSNE_cPCAs5$Y[,2]

Plot_tSNE <- ggplot(Master_D12_Cl) 

Plot_tSNE+ geom_point(aes(tSNE_1,tSNE_2, colour = STB_Index), size= 0.1, shape = 21, alpha = 0.3)+
  
scale_x_continuous(limits = c(-35, 35),
                     breaks = c(0,-10,-20,10,20)) +
scale_y_continuous(limits = c(-35, 35),
                     breaks = c(0,-10,-20,10,20)) +

xlab("tSNE 1")+
ylab("tSNE 2")+
#scale_color_manual(values = c("grey","orange","red","yellow", "turquoise","green","darkgreen"))+
#scale_color_brewer(palette = "Dark2")+
#scale_colour_gradient(low = "yellow", high = "red")+
scale_colour_gradient2(low = "red", mid = "yellow", high = "darkgreen", midpoint = 0)+
#facet_wrap(vars(Cell_Type))+
ECPT_theme()

```

With Density estimate
```{r}
# Master_D12_Cl$tSNE_1 <-A_tSNE_cPCAs5$Y[,1]
# Master_D12_Cl$tSNE_2 <-A_tSNE_cPCAs5$Y[,2]
#colourfactor<- Master_D12_Cl$Cell_Type
Plot_tSNE <- ggplot(Master_D12_Cl) 

Plot_tSNE+ geom_point(aes(tSNE_1,tSNE_2, colour=factor(Cell_Type)), size= 0.01, shape = 16, alpha =1)+
geom_density2d_filled(aes(tSNE_1,tSNE_2, fill= after_stat(level), alpha=0.3), bins=5, contour_var = "ndensity")+
scale_x_continuous(limits = c(-35, 35),
                     breaks = c(0,-10,-20,10,20)) +
scale_y_continuous(limits = c(-35, 35),
                     breaks = c(0,-10,-20,10,20)) +
#coord_cartesian(xlim = c(-15,7), ylim = c(7,17.5))+
xlab("tSNE 1") +
ylab("tSNE 2")+
#scale_colour_gradient2(low = "blue", mid = "red", high = "yellow", midpoint = 150)+
#scale_fill_gradient(low= "grey", high = "red")+
#scale_colour_manual(values = c("red", "green", "blue","black"))+
scale_fill_brewer(palette = "Greys")+
facet_wrap(vars(Cell_Type))+
ECPT_theme()
```
