---
title: "ECPT Data Import"
output: html_notebook
---

Libraries (packages must be installed on local computer with install.packages)
```{r}
library(DBI)
library(RSQLite)
library(tidyverse)
library(rlist)
library(data.table)
library(ggplot2)
library(ggstance)
library(scales)
library(ggpmisc) 
library(tidyr)
library(ggpubr)
library(psych)
library(purrr)
library(dplyr)
```

!!!
Following piece of script require mySQL data base. 
Chesnais et al. J Cell Sci 2022 data are available as tidy DF in R Data or .csv formats and can be imported directly by opening relative files (ECPT_DATA.rds or .csv) in project folder
!!!

Functions
```{r}
ExtractMetaData <- function(x) {
  tbl(x, "Per_Cell") %>%
  left_join(tbl(x, "Per_Image")) %>%
  select (Img_N = ImageNumber,
          Experiment = Image_Metadata_Experiment,
          Img_Nuclei_N = Image_Count_Nuclei,
          Cell_Type = Image_Metadata_Cell,
          Treatment = Image_Metadata_Treatment,
          Well = Image_Metadata_Well) %>%
            collect()
}

###

ExtractCellMorphology <- function(x){
  tbl(x, "Per_CellObjExp") %>%
            select (Img_N = ImageNumber,
              Cell_NCheck = CellObjExp_Number_Object_Number,
                    Cell_Area = CellObjExp_AreaShape_Area,
                    Cell_Perim = CellObjExp_AreaShape_Perimeter,
                    Cell_MaxL = CellObjExp_AreaShape_MajorAxisLength,
                    Cell_MinL = CellObjExp_AreaShape_MinorAxisLength,
                    Cell_Orientation = CellObjExp_AreaShape_Orientation,
                    Cell_Neighbour_N = CellObjExp_Neighbors_NumberOfNeighbors_Expanded,
                    Cell_1st_Nb_Dist = CellObjExp_Neighbors_FirstClosestDistance_Expanded,
                   Cell_2nd_Nb_Dist = CellObjExp_Neighbors_SecondClosestDistance_Expanded,
                    Perc_Touch = ) %>%
            collect()
}

###

ExtractNucleiInfo <- function(x){
  tbl(x, "Per_Nuclei") %>%
  select(Img_N = ImageNumber,
         Cell_NCheck = Nuclei_Number_Object_Number,
         Nu_X = Nuclei_Location_Center_X,
         Nu_Y = Nuclei_Location_Center_Y,
         DNA_IntI = Nuclei_Intensity_IntegratedIntensity_Nuclei,
         Nu_Clustering = Nuclei_Neighbors_NumberOfNeighbors_20,
         Nu_1st_Nb_Dist = Nuclei_Neighbors_FirstClosestDistance_20,
         Nu_2nd_Nb_Dist = Nuclei_Neighbors_SecondClosestDistance_20, Nu_Area = Nuclei_AreaShape_Area,
         Nu_NCH_IntI = Nuclei_Intensity_IntegratedIntensity_NOTCH,
         Nu_HEST_IntI = Nuclei_Intensity_IntegratedIntensity_HEST,
         Nu_NCH_IntI_Mean = Nuclei_Intensity_MeanIntensity_NOTCH,
         Nu_HEST_IntI_Mean = Nuclei_Intensity_MeanIntensity_HEST) %>%
  collect()
}

###

ExtractPercJ <- function(x){
  tbl(x, "Per_CellsObj") %>%
            select (Img_N = ImageNumber,
              Cell_NCheck = CellsObj_Number_Object_Number,
              Perc_J0 = CellsObj_Neighbors_PercentTouching_NaJ_Adjacent,
              Perc_J1 = CellsObj_Neighbors_PercentTouching_Class1_Adjacent,
              Perc_J2 = CellsObj_Neighbors_PercentTouching_Class2_Adjacent,
              Perc_J3 = CellsObj_Neighbors_PercentTouching_Class3_Adjacent,
              Perc_J4 = CellsObj_Neighbors_PercentTouching_Class4_Adjacent,
              Perc_J5 = CellsObj_Neighbors_PercentTouching_Class5_Adjacent,) %>%
            collect()
}

###

ExtractCytoInfo <- function(x){
  tbl(x, "Per_Cytoplasm") %>%
    select(Img_N = ImageNumber,
         Cell_NCheck = Cytoplasm_Number_Object_Number,Cy_NCH_IntI = Cytoplasm_Intensity_IntegratedIntensity_NOTCH,
           Cy_HEST_IntI = Cytoplasm_Intensity_IntegratedIntensity_HEST,
           Cy_NCH_IntI_Mean = Cytoplasm_Intensity_MeanIntensity_NOTCH,
           Cy_HEST_IntI_Mean = Cytoplasm_Intensity_MeanIntensity_HEST)
}
ExtractCytoInfo(CONNEX)

###

ExtractJuncSegs <- function(x) {
  tbl(x, "Per_JunctionSegments") %>%
  select (Img_N = ImageNumber,
          Junction_Number = JunctionSegments_Number_Object_Number,
          Junction_Length = JunctionSegments_AreaShape_Area,
          Class1 = JunctionSegments_Parent_Class1,
          Class2 = JunctionSegments_Parent_Class2,
          Class3 = JunctionSegments_Parent_Class3,
          Class4 = JunctionSegments_Parent_Class4,
          Class5 = JunctionSegments_Parent_Class5) %>%
            collect()
}

###

ExtractRelationships <- function(x) {
  tbl(x, "Per_Relationships") %>%
  select (Type_Id = relationship_type_id,
          Img_N = image_number1,
          Junction_Number = object_number1,
          Cell_Neighbour_Number = object_number2) %>%
            collect()
}

###

ExtractLMCells <- function(x) {
  tbl(x, "LM_Cells") %>%
  select (Img_N = ImageNumber,
          Cell_NCheck = CellObjExp_Number_Object_Number,
          Dividing = class) %>%
            collect()
}
```

Connect to MySQL Database
```{r}
#Substitute /path/data.db with user defined path pointing to database File
CONNEX <- dbConnect(RSQLite::SQLite(), "/path/data.db") 
```

Create Data Frame
```{r}
NucleiInfo <- ExtractNucleiInfo(CONNEX)
NucleiInfo$Un_Cell_Id <- paste(NucleiInfo$Img_N,'_',NucleiInfo$Cell_NCheck)
CytoInfo <- as.data.frame(ExtractCytoInfo(CONNEX))
CytoInfo$Un_Cell_Id <- paste(CytoInfo$Img_N,'_',CytoInfo$Cell_NCheck)
LMCells <- ExtractLMCells(CONNEX)
LMCells$Un_Cell_Id <- paste(LMCells$Img_N,'_',LMCells$Cell_NCheck)

InitialDF <- ExtractMetaData(CONNEX)[order(ExtractMetaData(CONNEX)$Img_N),] %>%
cbind(ExtractCellMorphology(CONNEX)[order(ExtractCellMorphology(CONNEX)$Img_N),])%>%
cbind(ExtractPercJ(CONNEX)[order(ExtractPercJ(CONNEX)$Img_N),])  

InitialDF$Un_Cell_Id <- paste(InitialDF$Img_N,'_',InitialDF$Cell_NCheck)
InitialDF[order(InitialDF$Un_Cell_Id),]

SecondDF <- InitialDF %>%
  cbind(NucleiInfo[order(NucleiInfo$Un_Cell_Id),]) %>%  
  cbind(CytoInfo[order(CytoInfo$Un_Cell_Id),]) %>%
  cbind(LMCells[order(LMCells$Un_Cell_Id),])

DF <- SecondDF[ , !duplicated(colnames(SecondDF))]

rm(InitialDF, SecondDF)
```

Calculate derived measures
```{r}
### Width to lenth ratio
DF$WLR <- (DF$Cell_MinL / DF$Cell_MaxL)
### Total NOTCH
DF <- DF %>% mutate(Tot_NCH = Nu_NCH_IntI + Cy_NCH_IntI)
### Tot HES
DF <- DF %>% mutate(Tot_HEST = x$Nu_HEST_IntI + x$Cy_HEST_IntI)

```
Removing donor tag from cell type
```{r}
#replicate to keep donor tag
DF$Donor <- DF$Cell_Type

#remove donor letters
DF$Cell_Type<-gsub("_D1","",as.character(DF$Cell_Type))
DF$Cell_Type<-gsub("_D2","",as.character(DF$Cell_Type))
```

Labels fixes (specific to Chesnais et al. J Cell Sci 2022)
```{r}
#Change VRGF to VEGF
DF$Treatment<-gsub("VRGF","VEGF",as.character(DF$Treatment))

#Change HPMED to HPMEC
DF$Cell_Type<-gsub("HPMED","HPMEC",as.character(DF$Cell_Type))

#Remove cell type from donor column
DF$Donor<-gsub("HUVEC_","",as.character(DF$Donor))
DF$Donor<-gsub("HPMEC_","",as.character(DF$Donor))
DF$Donor<-gsub("HAoEC_","",as.character(DF$Donor))
```

Create Junctions table and attach to Data Frame
```{r}
JunctionDF <- ExtractJuncSegs(CONNEX) %>%
  inner_join(ExtractRelationships(CONNEX)[which(ExtractRelationships(CONNEX)$Type_Id == '23'), ]) %>%
  subset(., select = -c(Type_Id))
JunctionDF$Un_Cell_Id <- paste(JunctionDF$Img_N,'_',JunctionDF$Cell_Neighbour_Number)

ClassChange <- function(x){
  x %>%
    mutate(Class1 = ifelse(.$Class1 == 0, "0", "1")) %>%
    mutate(Class2 = ifelse(.$Class2 == 0, "0", "1")) %>%
    mutate(Class3 = ifelse(.$Class3 == 0, "0", "1")) %>%
    mutate(Class4 = ifelse(.$Class4 == 0, "0", "1")) %>%
    mutate(Class5 = ifelse(.$Class5 == 0, "0", "1"))
}

JunctionDF3 <- ClassChange(JunctionDF)

JunctionDF3 <- JunctionDF3 %>%
subset(., select = c(Un_Cell_Id, Class1, Class2, Class3, Class4, Class5))

JunctionDF3$Class1 <- as.numeric(JunctionDF3$Class1)
JunctionDF3$Class2 <- as.numeric(JunctionDF3$Class2)
JunctionDF3$Class3 <- as.numeric(JunctionDF3$Class3)
JunctionDF3$Class4 <- as.numeric(JunctionDF3$Class4)
JunctionDF3$Class5 <- as.numeric(JunctionDF3$Class5)

JunctionDF4 <- JunctionDF3 %>%
  group_by(Un_Cell_Id) %>%
  summarise(Class1_Count = sum(Class1),
            Class2_Count = sum(Class2),
            Class3_Count = sum(Class3),
            Class4_Count = sum(Class4),
            Class5_Count = sum(Class5),
            Total_Junctions = sum(Class1_Count, Class2_Count, Class3_Count, Class4_Count, Class5_Count),
            Perc_Class1 = as.numeric(Class1_Count/Total_Junctions * 100),
            Perc_Class2 = as.numeric(Class2_Count/Total_Junctions * 100),
            Perc_Class3 = as.numeric(Class3_Count/Total_Junctions * 100),
            Perc_Class4 = as.numeric(Class4_Count/Total_Junctions * 100),
            Perc_Class5 = as.numeric(Class5_Count/Total_Junctions * 100))

JunctionDF4$Perc_Class1 <- format(round(JunctionDF4$Perc_Class1, 2), nsmall = 2)
JunctionDF4$Perc_Class2 <- format(round(JunctionDF4$Perc_Class2, 2), nsmall = 2)
JunctionDF4$Perc_Class3 <- format(round(JunctionDF4$Perc_Class3, 2), nsmall = 2)
JunctionDF4$Perc_Class4 <- format(round(JunctionDF4$Perc_Class4, 2), nsmall = 2)
JunctionDF4$Perc_Class5 <- format(round(JunctionDF4$Perc_Class5, 2), nsmall = 2)

rm(JunctionDF, JunctionDF3)

#Attach Junction Info
FinalDF <- DF %>%
  left_join(JunctionDF4)

rm(JunctionDF4, DF)
```

DF cleanup (Thresholds to be calibrated on experimental data)
```{r}
ECPT_Data <- FinalDF[FinalDF$Cell_Area<= 55000,]
ECPT_Data <- ECPT_Data[ECPT_Data$Nu_Area<= 5000,]
ECPT_Data <- ECPT_Data[ECPT_Data$Total_Junctions <=10 & ECPT_Data$Total_Junctions > 2,]
```

Normalise Intensity Data 
```{r}
###DNA Norm###
DNANorm <- left_join(ECPT_Data, (Normalise(ECPT_Data, ECPT_Data$DNA_IntI, Experiment, Cell_Type))) %>%
  select(NormFact) %>%
  collect()
ECPT_Data$DNANorm<-DNANorm$NormFact
ECPT_Data$DNA_IntI_Norm <- (ECPT_Data$DNA_IntI*ECPT_Data$DNANorm)
rm(DNANorm)
ECPT_Data$DNANorm<-NULL
###

###nu_NCH Norm###
NCHNorm <- left_join(ECPT_Data, (Normalise(ECPT_Data, ECPT_Data$Nu_NCH_IntI, Experiment, Cell_Type))) %>%
  select(NormFact) %>%
  collect()
ECPT_Data$NCHNorm<-NCHNorm$NormFact
ECPT_Data$NCH_IntI_Norm <- (ECPT_Data$Nu_NCH_IntI*ECPT_Data$NCHNorm)
rm(NCHNorm)
ECPT_Data$NCHNorm<-NULL
###

###Nu_HEST Norm###
HESTNorm <- left_join(ECPT_Data, (Normalise(ECPT_Data, ECPT_Data$Nu_HEST_IntI, Experiment, Cell_Type))) %>%
  select(NormFact) %>%
  collect()
ECPT_Data$HESTNorm<-HESTNorm$NormFact
ECPT_Data$HEST_IntI_Norm <- (ECPT_Data$Nu_HEST_IntI*ECPT_Data$HESTNorm)
rm(HESTNorm)
ECPT_Data$HESTNorm<-NULL

###Cy_NCH Norm###
CNCHNorm <- left_join(ECPT_Data_NoDAPT, (Normalise(ECPT_Data_NoDAPT, ECPT_Data_NoDAPT$Cy_NCH_IntI_Mean, Experiment, Cell_Type))) %>%
  select(NormFact) %>%
  collect()
ECPT_Data_NoDAPT$CNCHNorm<-CNCHNorm$NormFact
ECPT_Data_NoDAPT$CNCH_IntI_Norm <- (ECPT_Data_NoDAPT$Cy_NCH_IntI_Mean*ECPT_Data_NoDAPT$CNCHNorm)
rm(CNCHNorm)
ECPT_Data$CNCHNorm<-NULL
```

Assign cell cycle labels (Thresholds to be calibrated by inspection of DNA Intensity density distributions)
```{r}
ECPT_Data <- ECPT_Data %>%
    mutate(Cell_Cycle = ifelse(ECPT_Data$DNA_IntI_Norm <= 1200, "G0/G1", 
                                       ifelse(ECPT_Data$DNA_IntI_Norm > 1200 & ECPT_Data$DNA_IntI_Norm <= 1700, "S","G2/M")))

ECPT_Data <- ECPT_Data %>%
  mutate(Cell_Cycle = ifelse(ECPT_Data$Dividing == 'positive', "LM", .$Cell_Cycle))
```

```{r}
#J categories reassignemnt in correct order
ECPT_Data$PJ0 <- ECPT_Data$Perc_J5
ECPT_Data$PJ1 <- ECPT_Data$Perc_J1
ECPT_Data$PJ2 <- ECPT_Data$Perc_J3
ECPT_Data$PJ3 <- ECPT_Data$Perc_J2
ECPT_Data$PJ4 <- ECPT_Data$Perc_J4
ECPT_Data$PJ5 <- ECPT_Data$Perc_J0

ECPT_Data$Perc_J0<-ECPT_Data$Perc_J1<-ECPT_Data$Perc_J2<-ECPT_Data$Perc_J3<-ECPT_Data$Perc_J4<-ECPT_Data$Perc_J5<- NULL
######
```

```{r}
dbDisconnect(CONNEX)
```